SubGenome Analysis

### 2017-08-07 R/SubGenome Analysis.Rmd
Updated to point to renamed file

```{r importSynMapData, include=FALSE}
source("parseForSubgenomes.R")
```
```{r reportSynMapData, echo=FALSE, results="asis"}
# Report results of import
cat(sprintf("We have imported %d lines from the parsed SynMap file.", nrow(syntelogs.raw)))
```

>>>>

```{r importSynMapData, include=FALSE}
source("parseSubgenomes.R")
```
```{r reportSynMapData, echo=FALSE, results="asis"}
# Report results of import
cat(sprintf("We have imported %d lines from the parsed SynMap file.", nrow(syntelogs.raw)))
```
